Andres Karjus

### 2021-11-19 news.Rmd
news
refresh

@@

>>>>

- Gave a talk on linguistic corpora and experiments (and media&culture data) at the seminar of the Poncelet laboratory in Moscow (17.11.2021)

@@

- Presented a [poster "Capturing aesthetic complexity in art
using compression ensembles"](https://andreskarjus.github.io/talks/cultureconference2021/) (click for pdf) at [Culture Conference 2021](https://culture-conference.com/)
